Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
fix risk diff

    # Get pairwise comparisons on response scale (for risk differences)
    risk_diffs <- pairs(emm_response, reverse = TRUE,
                       by = c("dr_severity", "any_treatment"))

@@

    # Pool risk differences (probability scale)
    # Extract the j-th estimate from each imputation
    rd_estimates <- sapply(all_risk_diffs, function(x) {
      x$estimate[j]
    })

@@

# Store for visualization (use OR results for compatibility)
subgroup_effects_stored <- data.frame(
  DR_Severity = or_effects$dr_severity,
  Treatment = or_effects$any_treatment,
  Log_Odds = or_effects$log_odds,
  SE = or_effects$SE_log_odds,
  CI_Lower = or_effects$CI_Lower_log,
  CI_Upper = or_effects$CI_Upper_log,
  OR = or_effects$OR,
  OR_CI_Lower = or_effects$OR_CI_Lower,
  OR_CI_Upper = or_effects$OR_CI_Upper,
  P_Value = or_effects$p.value
)
```

@@

# Save key results for reporting
results_to_save <- list(
  pooled_coefficients = pooled_results,
  subgroup_effects = subgroup_effects_stored,
  emmeans_results = pooled_results,  # The emmeans-based effects
  probability_table = if(exists("prob_table")) prob_table else NULL,
  model_summaries = model_summaries,
  n_imputations = n_imputations,
  analysis_mode = analysis_mode,
  timestamp = Sys.time()
)

>>>>

    # Get pairwise comparisons on response scale (for risk differences)
    # Use regrid to ensure we get differences not ratios
    risk_diffs <- regrid(emm_response) |>
      pairs(reverse = TRUE, by = c("dr_severity", "any_treatment"))

@@

    # Pool risk differences (probability scale)
    # Extract the j-th estimate from each imputation
    # pairs() on response scale may use 'odds.ratio' or 'estimate' depending on emmeans version
    rd_estimates <- sapply(all_risk_diffs, function(x) {
      if ("estimate" %in% names(x)) {
        x$estimate[j]
      } else if ("odds.ratio" %in% names(x)) {
        # This is actually a risk difference despite the column name
        x$odds.ratio[j]
      } else {
        # Try to find the appropriate column
        stop("Could not find estimate column in risk diff results. Columns are: ", 
             paste(names(x), collapse = ", "))
      }
    })

@@

# Store for visualization (use OR results for compatibility)
subgroup_effects_stored <- data.frame(
  DR_Severity = or_effects$dr_severity,
  Treatment = or_effects$any_treatment,
  Log_Odds = or_effects$log_odds,
  SE = or_effects$SE_log_odds,
  CI_Lower = or_effects$CI_Lower_log,
  CI_Upper = or_effects$CI_Upper_log,
  OR = or_effects$OR,
  OR_CI_Lower = or_effects$OR_CI_Lower,
  OR_CI_Upper = or_effects$OR_CI_Upper,
  P_Value = or_effects$p.value
)

# Also store risk differences for reporting
risk_diff_effects_stored <- data.frame(
  DR_Severity = rd_effects$dr_severity,
  Treatment = rd_effects$any_treatment,
  Risk_Diff = rd_effects$risk_diff,
  SE = rd_effects$SE_risk_diff,
  CI_Lower = rd_effects$CI_Lower,
  CI_Upper = rd_effects$CI_Upper,
  P_Value = rd_effects$p.value
)

# Display the risk differences prominently
message("\n=== RISK DIFFERENCES (Probability Scale) ===")
print(rd_table)
```

@@

# Save key results for reporting
results_to_save <- list(
  pooled_coefficients = pooled_results,
  subgroup_effects = subgroup_effects_stored,
  risk_differences = risk_diff_effects_stored,  # Risk differences on probability scale
  emmeans_results = pooled_results,  # The emmeans-based effects
  probability_table = if(exists("prob_table")) prob_table else NULL,
  model_summaries = model_summaries,
  n_imputations = n_imputations,
  analysis_mode = analysis_mode,
  timestamp = Sys.time()
)
